Benchmarking of the Non-Relativistic Hydrodynamics Alogorithms in thornado

### 2017-01-30 Documents/Euler/Benchmarks1D/draft.tex
updated document

\section{Numerical Experiments}
Several tests were used to assess the accuracy of the integration method \cite{LiskaWendroff2003}. 
\begin{table}
\begin{center}
\begin{tabular}{ |c|c c c|c c c|c c| }
 \hline
 Test & $\rho_L$ & $u_L$ & $p_L$ & $\rho_R$ & $u_R$ & $p_R$ & $x_0$ & T \\
 \hline
 1 & 1 & 0 & 1 & 0.125 & 0 & 0.1 & 0.5 & 0.2 \\
 2 & 1 & 0.75 & 1 & 0.125 & 0 & 0.1 & 0.3 & 0.2 \\
 3 & 1 & -2 & 0.4 & 1 & 2 & 0.4 & 0.5 & 0.15 \\
 4 & 1 & 1 & $10^-6$ & 1 & -1 & $10^-6$ & 0.5 & 1 \\
 5 & 1 & -19.59745 & 1000 & 1 & -19.59745 & 0.01 & 0.8 & 0.012 \\
 6 & 5.99924 & 19.5975 & 460.894 & 5.99242 & -6.19633 & 46.095 & 0.4 & 0.035 \\
 7 & 1.4 & 0 & 1 & 1 & 0 & 1 & 0.5 & 2 \\
 8 & 1.4 & 0.1 & 1 & 1 & 0.1 & 1 & 0.5 & 2 \\
 9 & 0.1261192 & 8.9047029 & 782.92899 & 6.591493 & 2.2654207 & 3.1544874 & 0.5 & 0.0039 \\
10 & 5.6698 & 9.0299 & 100 & 1.0 & 0.0 & 1.0 & 0 & ? \\
11 & 5.6698 & −1.4701 & 100 & 1.0 & -10.5 & 1.0 & 0 & ? \\
 \hline
\end{tabular}
  \caption{table of tests}
  \label{tab:testtable}
\end{center}
\end{table}
$x_0$ refers to the position of the barrier. The computational domain is 0.0 to 1.0 in tests 1--8, 0.1 to 0.6 in test 9 \cite{LiskaWendroff2003}, -5 to 15 in test 10, and -15 to 5 in test 11 \cite{Leveque2002}.

Test 12 is an interacting blast waves test, computed on 0.0 to 1.0, with discontinuities at 0.1 and 0.9. At all positions, initial density is 1 and initial velocity is 0. Initial pressure is 1000 on the left, 0.01 in the center, and 100 on the right \cite{LiskaWendroff2003}.

\subsection{Test 1: Sod's Shock Tube}

First, the tests were run with values computed at different intervals; the method of integration is the same in each test. Between the two endpoints, 128, 256, 512, and 1024 points were computed for on each respective test. Figures~\ref{fig:dencellcomp_20}--\ref{fig:velcellcomp_20} show results of these tests:
\begin{figure}
  \begin{center}
    \includegraphics[width=.95\textwidth]{dencellcomp_20}
  \end{center}
  \caption{density}
  \label{fig:dencellcomp_20}
\end{figure}
%\newpage

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.425\textwidth]{prscellcomp_20} &
	  \includegraphics[width=.425\textwidth]{velcellcomp_20}
	\end{tabular}
  \end{center}
  \caption{pressure and velocity}
\end{figure}
%\newpage

@@

\begin{figure}[h]
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.4\textwidth]{den_T9.png} &
	  \includegraphics[width=.4\textwidth]{denT9zoom.png} \\
	  \includegraphics[width=.4\textwidth]{prs_T9.png} &	
      \includegraphics[width=.4\textwidth]{vel_T9.png}\\
	\end{tabular}	
  \end{center}
  \caption{}
\end{figure}

@@

\begin{figure}[h]
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.4\textwidth]{den_T10.png} &
	  \includegraphics[width=.4\textwidth]{den10zoom.png} \\
	  \includegraphics[width=.4\textwidth]{prs_T10.png} &	
	  \includegraphics[width=.4\textwidth]{prs10zoom.png} \\
      \includegraphics[width=.4\textwidth]{vel_T10.png} &	
      \includegraphics[width=.4\textwidth]{vel10zoom.png} \\
	\end{tabular}	
  \end{center}
  \caption{}
\end{figure}

@@

\begin{figure}[h]
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.4\textwidth]{den_T11.png} &
	  \includegraphics[width=.4\textwidth]{den11zoom.png} \\
	  \includegraphics[width=.4\textwidth]{prs_T11.png} &	
	  \includegraphics[width=.4\textwidth]{prs11zoom.png} \\
      \includegraphics[width=.4\textwidth]{vel_T11.png} &	
      \includegraphics[width=.4\textwidth]{vel11zoom.png} \\
	\end{tabular}	
  \end{center}
  \caption{}
\end{figure}

@@

>>>>

\section{Numerical Experiments}
Several tests were used to assess the accuracy of the integration method \cite{LiskaWendroff2003}. 
\begin{table}[h!]
\begin{center}
\begin{tabular}{ |c|c c c|c c c|c c| }
 \hline
 Test & $\rho_L$ & $u_L$ & $p_L$ & $\rho_R$ & $u_R$ & $p_R$ & $x_0$ & T \\
 \hline
 1 & 1 & 0 & 1 & 0.125 & 0 & 0.1 & 0.5 & 0.2 \\
 2 & 1 & 0.75 & 1 & 0.125 & 0 & 0.1 & 0.3 & 0.2 \\
 3 & 1 & -2 & 0.4 & 1 & 2 & 0.4 & 0.5 & 0.15 \\
 4 & 1 & 1 & $10^-6$ & 1 & -1 & $10^-6$ & 0.5 & 1 \\
 5 & 1 & -19.59745 & 1000 & 1 & -19.59745 & 0.01 & 0.8 & 0.012 \\
 6 & 5.99924 & 19.5975 & 460.894 & 5.99242 & -6.19633 & 46.095 & 0.4 & 0.035 \\
 7 & 1.4 & 0 & 1 & 1 & 0 & 1 & 0.5 & 2 \\
 8 & 1.4 & 0.1 & 1 & 1 & 0.1 & 1 & 0.5 & 2 \\
 9 & 0.1261192 & 8.9047029 & 782.92899 & 6.591493 & 2.2654207 & 3.1544874 & 0.5 & 0.0039 \\
10 & 5.6698 & 9.0299 & 100 & 1.0 & 0.0 & 1.0 & 0 & 1 \\
11 & 5.6698 & −1.4701 & 100 & 1.0 & -10.5 & 1.0 & 0 & 1 \\
 \hline
\end{tabular}
  \caption{table of tests}
  \label{tab:testtable}
\end{center}
\end{table}
$x_0$ refers to the position of the barrier. The computational domain is 0.0 to 1.0 in tests 1--8, 0.1 to 0.6 in test 9 \cite{LiskaWendroff2003}, -5 to 15 in test 10, and -15 to 5 in test 11 \cite{Leveque2002}.

Test 12 is an interacting blast waves test, computed on 0.0 to 1.0, with discontinuities at 0.1 and 0.9. At all positions, initial density is 1 and initial velocity is 0. Initial pressure is 1000 on the left, 0.01 in the center, and 100 on the right \cite{LiskaWendroff2003}.
%\clearpage
\subsection{Test 1: Sod's Shock Tube}

First, the tests were run with values computed at different intervals; the method of integration is the same in each test. Between the two endpoints, 128, 256, 512, and 1024 points were computed for on each respective test. Figures~\ref{fig:dencellcomp_20}--\ref{fig:pvcellcomp} show results of these tests:
\begin{figure}[h!]
  \begin{center}
    \includegraphics[width=.95\textwidth]{dencellcomp_20}
  \end{center}
  \caption{density}
  \label{fig:dencellcomp_20}
\end{figure}
%\newpage

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.425\textwidth]{prscellcomp_20} &
	  \includegraphics[width=.425\textwidth]{velcellcomp_20}
	\end{tabular}
  \end{center}
  \caption{pressure and velocity}
  \label{fig:pvcellcomp}
\end{figure}
%\newpage

@@

%\begin{figure}[h]
 % \begin{center}
	%\begin{tabular}{cc}
     % \includegraphics[width=.4\textwidth]{den_T9.png} &
	  %\includegraphics[width=.4\textwidth]{denT9zoom.png} \\
	  %\includegraphics[width=.4\textwidth]{prs_T9.png} &	
      %\includegraphics[width=.4\textwidth]{vel_T9.png}\\
	%\end{tabular}	
  %\end{center}
 % \caption{}
%\end{figure}

@@

\begin{figure}[h]
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.4\textwidth]{den_T10.png} &
	  \includegraphics[width=.4\textwidth]{den10zoom.png} \\
	  \includegraphics[width=.4\textwidth]{prs_T10.png} &	
	  \includegraphics[width=.4\textwidth]{prs10zoom.png} \\
      \includegraphics[width=.4\textwidth]{vel_T10.png} &	
      \includegraphics[width=.4\textwidth]{vel10zoom.png} \\
	\end{tabular}	
  \end{center}
  \caption{density, pressure, and velocity}
\end{figure}

@@

\begin{figure}[h]
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.4\textwidth]{den_T11.png} &
	  \includegraphics[width=.4\textwidth]{den11zoom.png} \\
	  \includegraphics[width=.4\textwidth]{prs_T11.png} &	
	  \includegraphics[width=.4\textwidth]{prs11zoom.png} \\
      \includegraphics[width=.4\textwidth]{vel_T11.png} &	
      \includegraphics[width=.4\textwidth]{vel11zoom.png} \\
	\end{tabular}	
  \end{center}
  \caption{density, pressure, and velocity}
\end{figure}

@@

\subsection{Test 13: Shock Entropy Waves}

This test was first run with 1000 cells to see the solution with high resolution. Subsequent tests all had 200 cells, with various values of the beta parameter. Again, the 3rd order, 1000 cell solution is called ``exact.''

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.78\textwidth]{1000.png}	
  \end{center}
  \caption{density, 1000 cells}
\end{figure}

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.425\textwidth]{10.png} &
	  \includegraphics[width=.425\textwidth]{10zoom.png}
	\end{tabular}
  \end{center}
  \caption{density, beta=10}
  \label{fig:pvcellcomp}
\end{figure}

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.425\textwidth]{50.png} &
	  \includegraphics[width=.425\textwidth]{50zoom.png}
	\end{tabular}
  \end{center}
  \caption{density, beta=50}
  \label{fig:pvcellcomp}
\end{figure}

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.425\textwidth]{300.png} &
	  \includegraphics[width=.425\textwidth]{300zoom.png}
	\end{tabular}
  \end{center}
  \caption{density, beta=300}
  \label{fig:pvcellcomp}
\end{figure}
